### 2021-10-21 submission/response_to_reviewers.md

* Problem with knowing *truth*
* All models/simulations are worthless
* Figures 4 and 5 show that removing rare sequences causes problems for statistical power (Figure 4) and false detection of differences (Figure 5B)

**In general, much of the interpretation of the results appears predicated on the idea that the rare variants represent real taxa. However, there is only limited evidence in support of this view. In the section "The nature of singletons", Dr. Schloss finds that singletons are more prevalent in more shallowly sequenced samples and that singletons in a sample are often also present in another sample. Dr. Schloss concludes that these singletons are thus likely real variants and the rest of the investigation seems somewhat predicated upon this interpretation. However, I am left with several questions:**

**(A) Are the correlations meaningfully representative of a trend across all samples, or are they driven by a small number of outlier samples? Providing support of these trends by plotting the scatterplots for each study would help assuage this concern.**

I appreciate the reviewer's concern that the correlations presented in Figure 1AC could be driven by outliers. It is worth noting that I used Spearman correlation coefficients, which are robust to the effects of outliers since it is a ranked-based test. As suggested, by the reviewer, I created two new figures, Figures S2 and S3, which shows the requested plots for the data in Fig 1AC. I think it's pretty clear that the trend is robust to outliers.
